### 2024-04-02 scripts/01-download_data.qmd
update

#### Preamble ####
# Purpose: Downloads and saves the data from from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas. 
# Author: Hari Lee Robledo
# Date: April 2 2023 
# Contact: hari.leerobledo@mail.utoronto.ca 
# License: MIT
# Pre-requisites: None

```{r}
#### Workspace setup ####
#install.packages()
library(tidyverse)
library(readr)
```

``` {r}
#### Download data ####

# Corrected URL to the raw CSV file
url <- "https://raw.githubusercontent.com/the-pudding/data/725dc18a59a055891dee25e85652f416b0065bdd/pockets/measurements.csv"

# Read the CSV file
raw_pockets_data <- read_csv(url)

```
```{r}
#### Save data ####
write_csv(
  x = raw_pockets_data,
  file = "data/raw_data/raw_pockets_data.csv"
)
```

### 2024-04-02 scripts/01-download_data.qmd
scripts

@@
 #### Preamble ####
-# Purpose: Downloads and saves the data from from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas. 
+# Purpose: Download and save the data from from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas. 
 # Author: Hari Lee Robledo
@@
 #### Download data ####
-
-# Corrected URL to the raw CSV file
-url <- "https://raw.githubusercontent.com/the-pudding/data/725dc18a59a055891dee25e85652f416b0065bdd/pockets/measurements.csv"
-
-# Read the CSV file
-raw_pockets_data <- read_csv(url)
+raw_pockets_data <-
+  read_csv(
+    "https://raw.githubusercontent.com/the-pudding/data/725dc18a59a055891dee25e85652f416b0065bdd/pockets/measurements.csv",
+    show_col_types = FALSE,
+    skip = 0
+  )
 
 ```
+
 ```{r}
@@
   x = raw_pockets_data,
-  file = "data/raw_data/raw_pockets_data.csv"
+  file = here::here("data/raw_data/raw_pockets_data.csv")
 )

### 2024-04-02 scripts/02-data_cleaning.qmd
scripts

#### Preamble ####
# Purpose: Clean the data from from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas.  
# Author: Hari Lee Robledo
# Date: April 2 2023 
# Contact: hari.leerobledo@mail.utoronto.ca 
# License: MIT
# Pre-requisites: 01-download_data.qmd

#### Workspace setup ####

#### Clean data ####

#### Save data ####

### 2024-04-03 paper/paper.qmd
download raw data

---
title: "Jean Pockets and Gender"
subtitle: "subtitle"
author: Hari Lee Robledo
thanks: "Code and data are available at: https://github.com/hari-lr/pockets-and-gender"
date: today
date-format: long
abstract: "An introductory sentence that is comprehensible to a wide audience.
A more detailed background sentence that is relevant to likely readers.
A sentence that states the general problem.
Sentences that summarize and then explain the main results.
A sentence about general context.
And finally, a sentence about the broader perspective"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# Introduction
3 paragraphs

# Data {#sec-data}

# Model

## Model set-up

### Model justification

# Results

# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

\newpage

\appendix

# Appendix {-}

# Additional data details

\newpage

# References

### 2024-04-03 scripts/01-download_data.qmd
download raw data

@@
 library(readr)
+library(jsonlite)
 ```
@@
 ``` {r}
-#### Download data ####
+#### Download measurements csv data ####
 raw_pockets_data <-
@@
 ```{r}
-#### Save data ####
+#### Save measurements csv data ####
 write_csv(
@@
 ```
+
+``` {r}
+#### Download measurements json data ####
+# Code referenced from:chat.openai.com 
+github_url <- "https://raw.githubusercontent.com/the-pudding/data/master/pockets/measurementRectangles.json"
+
+# Read the JSON data from GitHub into R
+json_data <- fromJSON(github_url)
+```
+
+```{r}
+#### Save measurements json data ####
+# Code referenced from: chat.openai.com
+json_string <- toJSON(json_data, pretty = TRUE)
+
+# Specify the file path
+file_path <- here::here("data/raw_data/raw_data.json")
+
+# Write the JSON data to the file
+writeLines(json_string, file_path)
+```

### 2024-04-03 paper/paper.qmd
update

@@
 date-format: long
-abstract: "An introductory sentence that is comprehensible to a wide audience.
-A more detailed background sentence that is relevant to likely readers.
-A sentence that states the general problem.
-Sentences that summarize and then explain the main results.
-A sentence about general context.
-And finally, a sentence about the broader perspective"
+abstract: "Fashion has long reflected and reinforced gender inequalities, with women's clothing often lacking functional pockets found in men's garments.
+A 2018 study by Jan Diehm & Amber Thomas on The Pudding revealed this discrepancy, highlighting inferior pocket functionality in women's jeans.
+This paper aims to reproduce these findings and explore if gender disparities extend to pricing.
+Using the same data, we analyze the correlation between prices of men's and women's jeans.
+Results suggest that women's jeans not only have smaller pockets but also tend to be more expensive.
+This study sheds light on gender inequalities in everyday products and their broader implications.
+[UPDATE]"
 format: pdf
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 # Introduction
-3 paragraphs
 
-# Data {#sec-data}
+Throughout history, women have faced numerous restrictions and limitations, often ingrained within societal norms and cultural practices.
+Among these limitations, the realm of fashion has served as both a reflection and an enforcer of gender-based inequalities.
+From ancient times to the modern era, clothing has been a means of expressing social status, cultural identity, and gender roles.
+However, while men's garments historically incorporated functional pockets, allowing them to carry essentials such as money, keys, and tools, women's clothing has often lacked this practical feature.
+Instead, women's garments have frequently been designed with form-fitting silhouettes, delicate fabrics, and ornamental details, prioritizing aesthetics over utility.
+
+[ADD RESEARCH AND HISTORICAL CONTEXT]
+
+In 2018, Jan Diehm & Amber Thomas published Womens´s Pockets are Inferior on The Pudding, a data-centric digital publication.
+In this paper, they "measured pockets in both men´s and women’s pants in 20 of the US’ most popular blue jeans brands" [CITE].
+And  "programmatically determined whether various everyday items could fit in an otherwise empty pocket in jeans that aren’t being worn" [CITE].
+Jan Diehm & Amber Thomas concluded that women´s pockets were less functional than men´s.
+
+Using the data from the previously described article, this paper will graphically reproduce the results and examine whether there is a correlation between the prices of men's jeans and women's jeans.
+This will help better understand if gender inequality is only reflected in the jean´s pockets or in pricing as well.
+The findings revealed that (SPECULATION) [women´s jeans do not only have the smaller and less functional pockets, but also tend to be more expensive]
+
+This paper is structured into the following sections: Data, which explains the collection and cleaning process; Results, presenting trends and correlations found in the data; Discussion, comparing and evaluating the data; and Conclusion, summarizing the findings.
+
+# Data 
+The data utilized in this paper was retrieved from The Pudding GitHub Site Portal, specifically the data collected by by Jan Diehm and Amber Thomas  [CITE].
+Data was collected, cleaned, and analyzed using the open-source statistical programming software R [@citeR].
+This process involved various packages within R, including tidyverse [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readxl` [@readxl], `tibble` [@tibble], `janitor` [@janitor], `KableExtra` [@kableExtra], `knitr` [@knitr], `ggbeeswarm` [@ggbeeswarm], and `ggrepel` [@ggrepel].
+A comprehensive description of the data gathering and cleaning process is provided in the following subsections.
+[MAKE SURE ALL LIBRARIES ARE CITED]
+
+[snap of raw data]
+
+## CSV Dataset and cleaning
+Explain how the data was collected and measured
+
+## JSON Dataset and cleaning
 
 # Model
+[TBD]
 
 ## Model set-up
-
-### Model justification
+## Model justification
 
@@
 ## First discussion point {#sec-first-point}
-
 ## Second discussion point
-
 ## Third discussion point
 
-## Weaknesses and next steps
+##Weaknesses and next steps
 
@@
 
-# Additional data details
-
 \newpage

### 2024-04-03 scripts/02-data_cleaning.qmd
update

@@
 
+```{r}
 #### Workspace setup ####
+library(tidyverse)
+library(jsonlite)
+library(readr)
+library(janitor)
+library(dplyr)
 
+```
+
+```{r}
 #### Clean data ####
 
-#### Save data ####
+# Code referenced from:https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html
+
+raw_pockets_data<-
+  read_csv(
+    file = here::here("data/raw_data/raw_pockets_data.csv"),
+    show_col_types = FALSE
+  )
+
+# Change the name of the raw data into the clean data
+cleaned_pockets_data <-
+  clean_names(raw_pockets_data)
+
+# Select the rows of interest
+cleaned_pockets_data <-
+  cleaned_pockets_data |>
+  select(
+    brand,
+    style,
+    men_women,
+    price
+  )
+
+cleaned_pockets_data
+
+# Clean json file (pocket area measurments)
+json_file <- here::here("data/raw_data/raw_data.json")
+
+# Read the JSON data from the file
+json_data <- fromJSON(json_file)
+
+# Change the name of the raw data into the clean data
+cleaned_json_data <-
+  clean_names(json_data)
+
+# Select the rows of interest
+cleaned_json_data <-
+  cleaned_json_data |>
+  select(
+    updated_style,
+    group,
+    price_group,
+    pocket_area
+  )
+
+cleaned_json_data 
+```
+
+```{r}
+#### Save cleaned data ####
+# Code referenced from:https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html
+
+# save cleaned pockets data 
+write_csv(
+  x = cleaned_pockets_data,
+  file = here::here("data/analysis_data/cleaned_pockets_data.csv")
+)
+
+# save json cleaned data
+
+# Change from json format to csv
+csv_file <- here::here("data/analysis_data/cleaned_json_data.csv")
+
+# Write the cleaned data frame to a CSV file
+write_csv(cleaned_json_data, csv_file)
+
+```

### 2024-04-04 scripts/01-download_data.qmd
update

@@
 # Read the JSON data from GitHub into R
-json_data <- fromJSON(github_url)
+pocket_area_data <- fromJSON(github_url)
 ```
@@
 # Code referenced from: chat.openai.com
-json_string <- toJSON(json_data, pretty = TRUE)
+json_string <- toJSON(pocket_area_data, pretty = TRUE)
 
 # Specify the file path
-file_path <- here::here("data/raw_data/raw_data.json")
+file_path <- here::here("data/raw_data/pocket_area_data.json")
 

### 2024-04-04 scripts/02-data_cleaning.qmd
update

@@
 # License: MIT
-# Pre-requisites: 01-download_data.qmd
+# Pre-requisites: 01-download_data.R
 
@@
 
-# Clean json file (pocket area measurments)
-json_file <- here::here("data/raw_data/raw_data.json")
+# Code referenced from: chat.openai.com
+
+# Clean json file (pocket area measurements)
+json_file <- here::here("data/raw_data/pocket_area_data.json")
 
 # Read the JSON data from the file
-json_data <- fromJSON(json_file)
+pocket_area_data <- fromJSON(json_file)
 
 # Change the name of the raw data into the clean data
-cleaned_json_data <-
-  clean_names(json_data)
+cleaned_pocket_area_data <-
+  clean_names(pocket_area_data)
 
 # Select the rows of interest
-cleaned_json_data <-
-  cleaned_json_data |>
+cleaned_pocket_area_data <-
+  cleaned_pocket_area_data |>
   select(
@@
 
-cleaned_json_data 
+cleaned_pocket_area_data
 ```
@@
 
-# save json cleaned data
+# save json cleaned data (pocket area measurements)
 

### 2024-04-04 scripts/02-data_cleaning.qmd
update

@@
 # Change from json format to csv
-csv_file <- here::here("data/analysis_data/cleaned_json_data.csv")
+csv_file <- here::here("data/analysis_data/cleaned_pocket_area_data.csv")
 
 # Write the cleaned data frame to a CSV file
-write_csv(cleaned_json_data, csv_file)
+write_csv(cleaned_pocket_area_data, csv_file)
 

### 2024-04-22 scripts/01-download_data.R
Convert R script

@@ -1,0 +1,55 @@
+#### Preamble ####
+# Purpose: Download and save the data from from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas. 
+# Author: Hari Lee Robledo
+# Date: April 2 2023 
+# Contact: hari.leerobledo@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: None
+
+```{r}
+#### Workspace setup ####
+#install.packages()
+library(tidyverse)
+library(readr)
+library(jsonlite)
+```
+
+``` {r}
+#### Download measurements csv data ####
+raw_pockets_data <-
+  read_csv(
+    "https://raw.githubusercontent.com/the-pudding/data/725dc18a59a055891dee25e85652f416b0065bdd/pockets/measurements.csv",
+    show_col_types = FALSE,
+    skip = 0
+  )
+```
+
+
+```{r}
+#### Save measurements csv data ####
+write_csv(
+  x = raw_pockets_data,
+  file = here::here("data/raw_data/raw_pockets_data.csv")
+)
+```
+
+``` {r}
+#### Download measurements json data ####
+# Code referenced from:chat.openai.com 
+github_url <- "https://raw.githubusercontent.com/the-pudding/data/master/pockets/measurementRectangles.json"
+
+# Read the JSON data from GitHub into R
+pocket_area_data <- fromJSON(github_url)
+```
+
+```{r}
+#### Save measurements json data ####
+# Code referenced from: chat.openai.com
+json_string <- toJSON(pocket_area_data, pretty = TRUE)
+
+# Specify the file path
+file_path <- here::here("data/raw_data/pocket_area_data.json")
+
+# Write the JSON data to the file
+writeLines(json_string, file_path)
+```

### 2024-04-22 scripts/02-data_cleaning.qmd
update

@@
 library(dplyr)
-
 ```
@@
 write_csv(cleaned_pocket_area_data, csv_file)
-
 ```

### 2024-04-22 paper/paper.qmd
update

@@
 This study sheds light on gender inequalities in everyday products and their broader implications.
-[UPDATE]"
+[UPDATE according to findings]"
 format: pdf
@@
 library(tidyverse)
+library(tibble)
+library(ggplot2)
+library(dplyr)
+library(janitor)
+library(kableExtra)
+
+## read in cleaned data 
+cleaned_pockets_data = read_csv(
+  file = here::here("data/analysis_data/cleaned_pockets_data.csv"),
+  show_col_types = FALSE
+)
+
+## read in cleaned data 
+cleaned_pocket_area_data = read_csv(
+  file = here::here("data/analysis_data/cleaned_pocket_area_data.csv"),
+  show_col_types = FALSE
+)
 ```
@@
 ## CSV Dataset and cleaning
-Explain how the data was collected and measured
+Explain how the data was collected and measured.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-cleaned_pockets_data
+#| tbl-cap: Sample of Cleaned Pockets Data
+
+# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
+
+head (cleaned_pockets_data, 5) |>
+  kable(
+    col.names = c("brand","style","men_women","price"),
+  booktabs = TRUE
+  )
+```
 
 ## JSON Dataset and cleaning
-
-# Model
-[TBD]
-
-## Model set-up
-## Model justification
 

### 2024-04-22 scripts/02-data_cleaning.R

@@ -58,10 +58,11 @@ cleaned_pocket_area_data <-
 cleaned_pocket_area_data <-
   cleaned_pocket_area_data |>
   select(
-    updated_style,
-    group,
-    price_group,
-    pocket_area
+    brand,
+    style,
+    menWomen,
+    pocket_area,
+    price,
   ) 
 
 cleaned_pocket_area_data

### 2024-04-22 scripts/02-data_cleaning.qmd
update pockect area file

@@
 # Change the name of the raw data into the clean data
-cleaned_pocket_area_data <-
+cleaned_area_data <-
   clean_names(pocket_area_data)
@@
 # Select the rows of interest
-cleaned_pocket_area_data <-
-  cleaned_pocket_area_data |>
+cleaned_area_data <-
+  cleaned_area_data |>
   select(
-    updated_style,
-    group,
-    price_group,
-    pocket_area
+    brand,
+    style,
+    men_women,
+    pocket_area,
+    price,
   )
 
-cleaned_pocket_area_data
+cleaned_area_data
 ```
@@
 # Change from json format to csv
-csv_file <- here::here("data/analysis_data/cleaned_pocket_area_data.csv")
+csv_file <- here::here("data/analysis_data/cleaned_area_data.csv")
 
 # Write the cleaned data frame to a CSV file
-write_csv(cleaned_pocket_area_data, csv_file)
+write_csv(cleaned_area_data, csv_file)
 ```

### 2024-04-22 paper/paper.qmd
clean

@@
 ## read in cleaned data 
-cleaned_pocket_area_data = read_csv(
-  file = here::here("data/analysis_data/cleaned_pocket_area_data.csv"),
+cleaned_area_data = read_csv(
+  file = here::here("data/analysis_data/cleaned_area_data.csv"),
   show_col_types = FALSE
@@
 ## JSON Dataset and cleaning
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-cleaned_area_data
+#| tbl-cap: Sample of Cleaned Pocket Area Data
+
+# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
+
+head (cleaned_area_data, 5) |>
+  kable(
+    col.names = c("brand","style","men_women","pocket_area","price"),
+  booktabs = TRUE
+  )
+```
 

### 2024-04-22 scripts/02-data_cleaning.qmd
clean
delete duplicated data

@@
 
-# Code referenced from:https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html
-
-raw_pockets_data<-
-  read_csv(
-    file = here::here("data/raw_data/raw_pockets_data.csv"),
-    show_col_types = FALSE
-  )
-
-# Change the name of the raw data into the clean data
-cleaned_pockets_data <-
-  clean_names(raw_pockets_data)
-
-# Select the rows of interest
-cleaned_pockets_data <-
-  cleaned_pockets_data |>
-  select(
-    brand,
-    style,
-    men_women,
-    price
-  )
-
-cleaned_pockets_data
-
 # Code referenced from: chat.openai.com
@@
     brand,
-    style,
     men_women,
+    price,
     pocket_area,
-    price,
   )
@@
 cleaned_area_data
+
 ```
@@
 #### Save cleaned data ####
-# Code referenced from:https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html
-
-# save cleaned pockets data 
-write_csv(
-  x = cleaned_pockets_data,
-  file = here::here("data/analysis_data/cleaned_pockets_data.csv")
-)
-
 # save json cleaned data (pocket area measurements)

### 2024-04-22 scripts/01-download_data.R

@@ -15,25 +15,6 @@ library(jsonlite)
 ```
 
 ``` {r}
-#### Download measurements csv data ####
-raw_pockets_data <-
-  read_csv(
-    "https://raw.githubusercontent.com/the-pudding/data/725dc18a59a055891dee25e85652f416b0065bdd/pockets/measurements.csv",
-    show_col_types = FALSE,
-    skip = 0
-  )
-```
-
-
-```{r}
-#### Save measurements csv data ####
-write_csv(
-  x = raw_pockets_data,
-  file = here::here("data/raw_data/raw_pockets_data.csv")
-)
-```
-
-``` {r}
 #### Download measurements json data ####
 # Code referenced from:chat.openai.com 
 github_url <- "https://raw.githubusercontent.com/the-pudding/data/master/pockets/measurementRectangles.json"

### 2024-04-22 scripts/01-download_data.R
update

@@ -33,4 +33,13 @@ file_path <- here::here("data/raw_data/pocket_area_data.json")
 
 # Write the JSON data to the file
 writeLines(json_string, file_path)
+
+
+# Convert JSON to data frame
+df <- as.data.frame(pocket_area_data)
+
+# Save data frame as CSV
+write.csv(df, "pocket_area_data.csv", row.names = FALSE)
+
+
 ```

### 2024-04-22 scripts/01-download_data.R
update

@@ -39,7 +39,6 @@ writeLines(json_string, file_path)
 df <- as.data.frame(pocket_area_data)
 
 # Save data frame as CSV
-write.csv(df, "pocket_area_data.csv", row.names = FALSE)
-
-
+write.csv(df, "data/raw_data/pocket_area_data.csv", row.names = FALSE)
 ```
+

### 2024-04-23 paper/paper.qmd
update

--- 2024-04-03 paper/paper.qmd
@@
 library(tidyverse)
+library(tibble)
+library(ggplot2)
+library(dplyr)
+library(janitor)
+library(kableExtra)
+
+## read in raw data 
+pocket_area_data = read_csv(
+  file = here::here("data/raw_data/pocket_area_data.csv"),
+  show_col_types = FALSE
+)
+
+## read in cleaned data 
+cleaned_area_data = read_csv(
+  file = here::here("data/analysis_data/cleaned_area_data.csv"),
+  show_col_types = FALSE
+)
+
+women_jeans_data = read_csv(
+  file = here::here("data/analysis_data/women_jeans_data.csv"),
+  show_col_types = FALSE
+)
+
+men_jeans_data = read_csv(
+  file = here::here("data/analysis_data/men_jeans_data.csv"),
+  show_col_types = FALSE
+)
 ```
+
+\newpage
 
@@
 
-[snap of raw data]
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-raw_data
+#| tbl-cap: "Sample of Raw Pocket Area, Price and Gender Data"
 
-## CSV Dataset and cleaning
-Explain how the data was collected and measured
+head(pocket_area_data, 5)
+
+```
 
 ## JSON Dataset and cleaning
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-cleaned_area_data
+#| tbl-cap: "Sample of Cleaned Pocket Area, Price and Gender Data"
+
+# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
+
+head (cleaned_area_data, 5) |>
+  kable(
+    col.names = c("brand","men_women","price","pocket_area"),
+  booktabs = TRUE
+  )
+```
 
 # Model
-[TBD]
+Given the similarity in lightness observed in foundation shades across both countries, it was of interest to investigate if any differences in saturation existed.
+This investigation was motivated by the fact that the local population in each country has unique undertones.
+Before conducting the analysis, several tests were conducted to verify that the model assumptions (See Appendix A), including linearity, normality, and homoscedasticity of residuals, were satisfied, thereby ensuring that the model was well-suited for the data at hand.
 
-## Model set-up
-## Model justification
+The null hypothesis: there is no significant linear relationship between the lightness of foundation shades and the saturation of undertones.
+
+The alternative hypothesis: there is a significant linear relationship between the lightness of foundation shades and the saturation of undertones.
+
+A linear regression analysis can be conducted to test this hypothesis and to determine whether a statistically significant relationship exists between the variables.
+A low p-value for the regression coefficient for saturation would provide evidence against the null hypothesis, indicating that changes in saturation do result in a meaningful variation in lightness across foundation shades.
+On the other hand, if the p-value is high, this would suggest that there is not enough evidence to reject the null hypothesis, and there may be no significant linear relationship between the variables.
+Ultimately, the results of the analysis will inform whether the null hypothesis can be rejected or not.
+The mathematical equation for the linear regression model can be written as:
+
+$$L = \beta_0 + \beta_1S + \epsilon$$
+
+Where:
+
+- $L$ represents the dependent variable, which is the overall lightness of the foundation shade
+- $S$ represents the independent variable, which is the saturation of the foundation shade
+- $\beta_0$ represents the intercept of the regression line, which is the predicted value of $L$ when $S$ is equal to zero
+- $\beta_1$ represents the slope of the regression line, which is the change in $L$ for a one-unit increase in $S$
+- $\epsilon$ represents the random error term, which accounts for variability in $L$ that is not explained by the relationship with $S$
+
+The aim of linear regression is to estimate the values of $\beta_0$ and $\beta_1$ that minimize the sum of squared errors between the predicted and actual values of lightness ($L$) for the given values of saturation ($S$) in the dataset.
+By minimizing this sum of squared errors, the linear regression model can produce the best-fit line to describe the linear relationship between the two variables, allowing for the estimation of $L$ values based on known $S$ values.
+
+In this project, the lightness variable ($L$) is measured on a scale of 0 to 100, while the saturation variable ($S$) is measured on a scale of 0 to 1.
+Therefore, the slope coefficient $\beta_1$ in the linear regression model would represent the change in lightness ($L$) for a one-unit increase in saturation ($S$), where a one-unit increase in $S$ corresponds to an increase of 1/100 in the saturation of the foundation shade.
+The intercept $\beta_0$ in the model would represent the expected value of $L$ when $S$ is equal to zero, which in this case would correspond to the lightness value for a completely desaturated foundation shade.
+
+\newpage
 
 # Results
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-price_per_pocket_men
+#| fig-cap: "Jean Price vs Pocket Size (Men)"
+
+# Create plot for men_jeans_data
+men_jeans_plot <- ggplot(men_jeans_data, aes(x = pocket_area, y = price)) +
+  geom_point(color = "blue") +
+  geom_smooth(method = lm, se = FALSE) +
+  labs(
+    title = "Pocket Area and Price for Men's Jeans",
+    x = "Pocket Area (square pixels)",
+    y = "Price"
+  ) +
+  theme_classic()
+
+# Print the plot
+men_jeans_plot
+
+# Fit a linear regression model
+model <- lm(price ~ pocket_area, data = men_jeans_data)
+
+# View the summary of the model
+summary(model)
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-price_per_pocket_women
+#| fig-cap: "Jean Price vs Pocket Size (Women)"
+
+# Create plot for men_jeans_data
+women_jeans_plot <- ggplot(women_jeans_data, aes(x = pocket_area, y = price)) +
+  geom_point(color = "blue") +
+  geom_smooth(method = lm, se = FALSE) +
+  labs(
+    title = "Pocket Area and Price for Women's Jeans",
+    x = "Pocket Area (square pixels)",
+    y = "Price"
+  ) +
+  theme_classic()
+
+# Print the plot
+women_jeans_plot
+
+# Fit a linear regression model
+model <- lm(price ~ pocket_area, data = women_jeans_data)
+
+# View the summary of the model
+summary(model)
+
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-price_per_pocket_gender
+#| fig-cap: "Jean Price vs. Pocket Area Size per Gender"
+
+## Comparing between average building scores vs.average total income per ward
+
+#Code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
+
+cleaned_area_data |>
+  ggplot(aes(x = pocket_area, y = price, color = men_women)) + 
+  geom_point() + 
+  geom_smooth(method=lm, se=FALSE) + 
+  labs(
+    title = "Pocket Area and Price by Gender",
+    x = "Pocket Area (square pixels)",
+    y = "Price",
+    color = "Gender"
+  ) +
+  scale_color_manual(values = c("blue", "red")) +  # Set custom colors
+  theme_classic()
+```
 

### 2024-04-23 paper/paper.qmd
update

@@
 From ancient times to the modern era, clothing has been a means of expressing social status, cultural identity, and gender roles.
-However, while men's garments historically incorporated functional pockets, allowing them to carry essentials such as money, keys, and tools, women's clothing has often lacked this practical feature.
-Instead, women's garments have frequently been designed with form-fitting silhouettes, delicate fabrics, and ornamental details, prioritizing aesthetics over utility.
+According to design expert, Hannah Carlson, pocket inequality stems from the way clothes are designed and made, she explains that "From a very early age, I think we sort of agree as a culture that womenswear, girlswear is meant to be pretty," she said.
+"And menswear, boyswear is meant to be utilitarian" [@carlson].
+Men's garments historically incorporated functional pockets, allowing them to carry essentials such as money, keys, and tools, women's clothing has often lacked this practical feature.
+Instead, women's garments have frequently been designed with form-fitting silhouettes, delicate fabrics, and ornamental details, prioritizing aesthetics over utility.However, the 1880s, women began to be vocal about pocket inequality, as the "demand for the vote and the demand for pockets were made together" [@carlson].
 
-[ADD RESEARCH AND HISTORICAL CONTEXT]
-
-In 2018, Jan Diehm & Amber Thomas published Womens´s Pockets are Inferior on The Pudding, a data-centric digital publication.
-In this paper, they "measured pockets in both men´s and women’s pants in 20 of the US’ most popular blue jeans brands" [CITE].
-And  "programmatically determined whether various everyday items could fit in an otherwise empty pocket in jeans that aren’t being worn" [CITE].
-Jan Diehm & Amber Thomas concluded that women´s pockets were less functional than men´s.
+In 2018, Jan Diehm & Amber Thomas published Womens´s Pockets are Inferior on *The Pudding*, a data-centric digital publication.
+In this paper, they "measured pockets in both men´s and women’s pants in 20 of the US’ most popular blue jeans brands" [@pudding].
+They "programmatically determined whether various everyday items could fit in an otherwise empty pocket in jeans that aren’t being worn" [@pudding] and concluded that women´s pockets were less functional than men´s.
 
 Using the data from the previously described article, this paper will graphically reproduce the results and examine whether there is a correlation between the prices of men's jeans and women's jeans.
-This will help better understand if gender inequality is only reflected in the jean´s pockets or in pricing as well.
-The findings revealed that (SPECULATION) [women´s jeans do not only have the smaller and less functional pockets, but also tend to be more expensive]
+The study seeks to determine if women's jeans not only have smaller and less functional pockets but also tend to be more expensive.
+This will help better understand if gender inequality is only reflected in the jean's pockets or in pricing as well.
+The findings revealed that pocket area alone may not be a strong predictor of jeans prices for either gender, and there may be other factors influencing the pricing of jeans.
+A linear regression analysis revealed divergent findings regarding the relationship between pocket area and price in men's and women's jeans.
+For men's jeans, no significant correlation was found between pocket area and price, indicating that changes in pocket size do not significantly affect the price of men's jeans.
+In contrast, although a negative correlation was observed in women's jeans, it was not statistically significant, suggesting that while larger pocket areas might be associated with slightly lower prices, other factors likely play a more influential role in determining the price of women's jeans.
 

### 2024-04-24 paper/paper.qmd
update

--- 2024-04-22 paper/paper.qmd
@@
 This study sheds light on gender inequalities in everyday products and their broader implications.
-[UPDATE according to findings]"
+[UPDATE according to findingsThe findings revealed that pocket area alone may not be a strong predictor of jeans prices for either gender, and there may be other factors influencing the pricing of jeans.]"
 format: pdf
@@
 
-## read in cleaned data 
-cleaned_pockets_data = read_csv(
-  file = here::here("data/analysis_data/cleaned_pockets_data.csv"),
+## read in raw data 
+pocket_area_data = read_csv(
+  file = here::here("data/raw_data/pocket_area_data.csv"),
   show_col_types = FALSE
@@
 )
+
+women_jeans_data = read_csv(
+  file = here::here("data/analysis_data/women_jeans_data.csv"),
+  show_col_types = FALSE
+)
+
+men_jeans_data = read_csv(
+  file = here::here("data/analysis_data/men_jeans_data.csv"),
+  show_col_types = FALSE
+)
 ```
+
+\newpage
 
@@
 From ancient times to the modern era, clothing has been a means of expressing social status, cultural identity, and gender roles.
-However, while men's garments historically incorporated functional pockets, allowing them to carry essentials such as money, keys, and tools, women's clothing has often lacked this practical feature.
-Instead, women's garments have frequently been designed with form-fitting silhouettes, delicate fabrics, and ornamental details, prioritizing aesthetics over utility.
+According to design expert, Hannah Carlson, pocket inequality stems from the way clothes are designed and made, she explains that: "From a very early age, I think we sort of agree as a culture that womenswear, girlswear is meant to be pretty," she said.
+"And menswear, boyswear is meant to be utilitarian" [@carlson].
+Men's garments historically incorporated functional pockets, allowing them to carry essentials such as money, keys, and tools, women's clothing has often lacked this practical feature.
+Instead, women's garments have frequently been designed with form-fitting silhouettes, delicate fabrics, and ornamental details, prioritizing aesthetics over utility.However, the 1880s, women began to be vocal about pocket inequality, as the "demand for the vote and the demand for pockets were made together" [@carlson].
 
-[ADD RESEARCH AND HISTORICAL CONTEXT]
-
-In 2018, Jan Diehm & Amber Thomas published Womens´s Pockets are Inferior on The Pudding, a data-centric digital publication.
-In this paper, they "measured pockets in both men´s and women’s pants in 20 of the US’ most popular blue jeans brands" [CITE].
-And  "programmatically determined whether various everyday items could fit in an otherwise empty pocket in jeans that aren’t being worn" [CITE].
-Jan Diehm & Amber Thomas concluded that women´s pockets were less functional than men´s.
+In 2018, Jan Diehm & Amber Thomas published Womens´s Pockets are Inferior on *The Pudding*, a data-centric digital publication.
+In this paper, they "measured pockets in both men´s and women’s pants in 20 of the US’ most popular blue jeans brands" [@pudding].
+They "programmatically determined whether various everyday items could fit in an otherwise empty pocket in jeans that aren’t being worn" [@pudding]., and concluded that women´s pockets were less functional than men´s.
 
 Using the data from the previously described article, this paper will graphically reproduce the results and examine whether there is a correlation between the prices of men's jeans and women's jeans.
-This will help better understand if gender inequality is only reflected in the jean´s pockets or in pricing as well.
-The findings revealed that (SPECULATION) [women´s jeans do not only have the smaller and less functional pockets, but also tend to be more expensive]
+The study seeks to determine if women's jeans not only have smaller and less functional pockets but also tend to be more expensive.
+This will help better understand if gender inequality is only reflected in the jean's pockets or in pricing as well.
+A linear regression analysis revealed divergent findings regarding the relationship between pocket area and price in men's and women's jeans.
+For men's jeans, no significant correlation was found between pocket area and price, indicating that changes in pocket size do not significantly affect the price of men's jeans.
+In contrast, although a negative correlation was observed in women's jeans, it was not statistically significant, suggesting that while larger pocket areas might be associated with slightly lower prices, other factors likely play a more influential role in determining the price of women's jeans.
 
@@
 # Data 
-The data utilized in this paper was retrieved from The Pudding GitHub Site Portal, specifically the data collected by by Jan Diehm and Amber Thomas  [CITE].
+The data utilized in this paper was retrieved from The Pudding GitHub Site Portal, specifically the data collected by Jan Diehm and Amber Thomas  [@pudding].
 Data was collected, cleaned, and analyzed using the open-source statistical programming software R [@citeR].
-This process involved various packages within R, including tidyverse [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readxl` [@readxl], `tibble` [@tibble], `janitor` [@janitor], `KableExtra` [@kableExtra], `knitr` [@knitr], `ggbeeswarm` [@ggbeeswarm], and `ggrepel` [@ggrepel].
+This process involved various packages within R, including `tidyverse` [@tidyverse], `jsonlite` [@jsonlite], `readr` [@readr], `janitor` [@janitor], `dplyr` [@dplyr], `tibble` [@tibble], `ggplot2` [@ggplot2], `knitr` [@knitr], and `kableExtra` [@kableExtra].
 A comprehensive description of the data gathering and cleaning process is provided in the following subsections.
-[MAKE SURE ALL LIBRARIES ARE CITED]
 
-[snap of raw data]
+## Dataset
 
-## CSV Dataset and cleaning
-Explain how the data was collected and measured.
+In the original study, researchers examined jean pocket sizes across 20 brands, encompassing both men's and women's jeans, including skinny and straight styles.
+The assessment involved scrutinizing four pairs of jeans per brand, all tailored with a 32-inch waistband, despite falling below the median waist size for women in the US.
+Measurements were meticulously taken in physical stores located in Nashville, New York, and Seattle, with pocket dimensions recorded while jeans were unbuttoned and unzipped, from the inside [@pudding].
+The study incorporated computer-generated images to illustrate pocket curvature.
+Various objects, such as standard pen sizes and a front pocket wallet, were utilized to evaluate pocket compatibility.
+Additionally, area measurements were computed using the `d3.polygonArea()` function in d3.v4, offering valuable insights into the spatial characteristics of the jean pockets.
+These methods were intended to give a complete understanding of jean pocket sizes and how well they can hold everyday items.
+[@pudding].
+
+In this paper, the dataset used for analysis was obtained from `measurementRectangles.json`.
+This dataset mirrors the measurements found in `measurements.csv`, including brand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data).
+Notably, the dataset contains a "pocketArea" column representing the area of the polygon generated from a pocket's measurements.
+However, it's important to note that the units of measurement for this area are not explicitly specified in the provided metadata.
+To determine the units, one must examine how the measurements were collected and processed.
+Since the measurements were processed using computer-generated calculations and intended for web display, it is possible that the pocket area is denoted in square centimeters (px²).
+However, without explicit confirmation from the data documentation or creators of the dataset, absolute certainty regarding the units of measurement remains elusive.
 
@@
 #| echo: false
-#| label: tbl-cleaned_pockets_data
-#| tbl-cap: Sample of Cleaned Pockets Data
+#| label: tbl-raw_data
+#| tbl-cap: "Sample of Raw Jean Pockets Data"
 
-# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
+# Code referenced from: https://chat.openai.com/
+# Select the first five variables from your dataset
+data_subset <- select(pocket_area_data, 1:6)
 
-head (cleaned_pockets_data, 5) |>
+# Print the table using kable
+head (data_subset, 5) |>
    kable( 
-    col.names = c("brand","style","men_women","price"),
+      format = "markdown",
+      col.names = c("Brand", "Style", "Men/Women", "Name", "Fabric","Price"),
+      align = c("l", rep("c", 4))
+)
+```
+
+## Data Cleaning
+
+Initially, the code read the JSON data containing pocket area measurements, standardized the column names using the `clean_names()` function, and stored the cleaned data in the `cleaned_area_data` dataframe.
+Subsequently, the data was filtered based on gender, separating jeans intended for women and men using the `filter()` function.
+Only the "price" and "pocket_area" columns were retained for further analysis in the resulting dataframes `men_jeans_data` and `women_jeans_data` (see @tbl-menwomen_table), respectively.
+In the final step, the cleaned data was saved into CSV files.
+The `write.csv()` function was utilized to export the data, with separate CSV files generated for women's and men's jeans.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-menwomen_table
+#| layout-ncol: 2
+#| tbl-cap: "Sample of Cleaned Men's and Women´s Data"
+
+# Code referenced from: https://chat.openai.com/
+# Create tables
+head(men_jeans_data, 5) |>
+  kable(
+    format = "markdown",
+    caption = "Men's Data",
+    col.names = c("Price", "Pocket Area"),
+    booktabs = TRUE
+  )
+
+head(women_jeans_data, 5) |>
+  kable(
+    format = "markdown",
+    caption = "Women's Data",
+    col.names = c("Price", "Pocket Area"),
     booktabs = TRUE
@@
 
-## JSON Dataset and cleaning
+To visually explore the relationship between pocket area and price for both men's (see @fig-price_per_pocket_men) and women's jeans (see @fig-price_per_pocket_women), scatter plots with regression lines were created.
+
 ```{r}
@@
 #| echo: false
-#| label: tbl-cleaned_area_data
-#| tbl-cap: Sample of Cleaned Pocket Area Data
+#| label: fig-price_per_pocket_men
+#| fig-cap: "Jean Price vs Pocket Size (Men)"
 
-# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
+# Create plot for men_jeans_data
+men_jeans_plot <- ggplot(men_jeans_data, aes(x = pocket_area, y = price)) +
+  geom_point(color = "blue") +
+  geom_smooth(method = lm, se = FALSE) +
+  labs(
+    title = "Pocket Area and Price for Men's Jeans",
+    x = "Pocket Area",
+    y = "Price"
+  ) +
+  theme_classic()
 
-head (cleaned_area_data, 5) |>
-  kable(
-    col.names = c("brand","style","men_women","pocket_area","price"),
-  booktabs = TRUE
-  )
+# Print the plot
+men_jeans_plot
+
+# Standard deviation of price for men's jeans
+men_price_sd <- sd(men_jeans_data$price)
+
 ```
 
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-price_per_pocket_women
+#| fig-cap: "Jean Price vs Pocket Size (Women)"
+
+# Create plot for men_jeans_data
+women_jeans_plot <- ggplot(women_jeans_data, aes(x = pocket_area, y = price)) +
+  geom_point(color = "red") +
+  geom_smooth(method = lm, se = FALSE) +
+  labs(
+    title = "Pocket Area and Price for Women's Jeans",
+    x = "Pocket Area",
+    y = "Price"
+  ) +
+  theme_classic()
+
+# Print the plot
+women_jeans_plot
+
+# Standard deviation of price for women's jeans
+women_price_sd <- sd(women_jeans_data$price)
+```
+
+These plots visually depict the relationship between pocket area and price for men's and women's jeans.
+Additionally, to compute the standard deviation of price for both men's and women's jeans, the `sd()` function can be applied to the respective columns in the `men_jeans_data` and `women_jeans_data` dataframes.
+The standard deviation of price for women's jeans is 48.79, while for men's jeans, it is 40.49, indicating the variability in prices within each gender category.
+This measure helps assess the spread of prices around the mean and provides insight into the degree of dispersion in price values among the observed jeans.
+
+# Model
+To gain further insights and make predictions about [], we will be implementing a linear regression model.
+
+The final model is displayed here.
+
+$$L = \beta_0 + \beta_1S + \epsilon$$
+
+Where:
+
+- $L$ represents the dependent variable, which is the overall price of jeans
+- $S$ represents the independent variable, which is the pocket area
+- $\beta_0$ represents the intercept of the regression line, which is the predicted value of $L$ when $S$ is equal to zero
+- $\beta_1$ represents the slope of the regression line, which is the change in $L$ for a one-unit increase in $S$
+- $\epsilon$ represents the random error term, which accounts for variability in $L$ that is not explained by the relationship with $S$
+
+Linear regression seeks to determine the optimal parameters $\beta_0$ and $\beta_1$ that minimize the discrepancies between predicted and observed prices across varying pocket areas in the dataset.
+Through this minimization process, the model constructs a line that most accurately represents the association between pocket area and price.
+Consequently, we can predict price values based on known pocket area measurements.
+This regression analysis sheds light on how pocket area influences the pricing of jeans for both men and women, offering valuable insights into the pricing dynamics within each gender category.
+
 # Results
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-men_model_summary
+#| tbl-cap: "Summary of Linear Regression Model for Men's Jeans"
+# Fit a linear regression model for men's jeans
+men_model <- lm(price ~ pocket_area, data = men_jeans_data)
+
+# View the summary of the model
+summary_men <- summary(men_model)
+summary_table_men <- summary_men$coefficients
+
+# Print the summary table
+kable(summary_table_men, caption = "Summary of Linear Regression Model for Men's Jeans", align = "c")
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-women_model_summary
+#| tbl-cap: "Summary of Linear Regression Model for Women's Jeans"
+# Fit a linear regression model for women's jeans
+women_model <- lm(price ~ pocket_area, data = women_jeans_data)
+
+# View the summary of the model
+summary_women <- summary(women_model)
+summary_table_women <- summary_women$coefficients
+
+# Print the summary table
+kable(summary_table_women, caption = "Summary of Linear Regression Model for Women's Jeans", align = "c")
+```
+
+A scatterplot was generated to compare pocket area and price for both men's and women's jeans.
+Each gender category was represented by a distinct color in the plot.
+Additionally, linear regression lines were overlaid for each gender group to observe potential differences in the relationship between pocket area and price.
+
+This visualization facilitated the comparison of how pocket area related to price for men's and women's jeans separately.
+By including separate regression lines for each gender, we could assess the direction and strength of the relationship between these variables within each group.
+The use of different colors for men and women aided in distinguishing between the two groups, enabling easy interpretation of the plot.
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-price_per_pocket_gender
+#| fig-cap: "Jean Price vs. Pocket Area Size per Gender"
+
+## Comparing between average building scores vs.average total income per ward
+
+#Code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
+
+cleaned_area_data |>
+  ggplot(aes(x = pocket_area, y = price, color = men_women)) + 
+  geom_point() + 
+  geom_smooth(method=lm, se=FALSE) + 
+  labs(
+    title = "Pocket Area and Price by Gender",
+    x = "Pocket Area (square pixels)",
+    y = "Price",
+    color = "Gender"
+  ) +
+  scale_color_manual(values = c("blue", "red")) + theme_classic()
+```
+
+After visualizing the linear regression for both men's and women's jeans, I proceeded to analyze the results obtained from the regression models:
+
+The linear regression models for both men's and women's jeans revealed interesting insights into the relationship between pocket area and price.
+
+For men's jeans, the coefficient estimate for pocket area ($\beta_1$) is -0.002286, indicating a very small and statistically insignificant negative association between pocket area and price.
+This suggests that, on average, changes in pocket area do not have a significant impact on the price of men's jeans.
+The p-value associated with the pocket area coefficient is 0.6445, which is much greater than the typical significance level of 0.05.
+Additionally, the \( R^2 \) value, which measures the proportion of variance in the dependent variable explained by the independent variable, is very low at 0.005662.
+Overall, these results suggest that there is little evidence to suggest a meaningful relationship between pocket area and price for men's jeans.
+
+In contrast, for women's jeans, the coefficient estimate for pocket area is -0.009345, also indicating a small negative association with price, although it is slightly larger in magnitude compared to men's jeans.
+However, like men's jeans, this coefficient is statistically insignificant with a p-value of 0.1804.
+The \( R^2 \) value for women's jeans is slightly higher at 0.04671, indicating that pocket area explains a slightly larger proportion of the variance in price compared to men's jeans.
+Despite this, the overall relationship between pocket area and price remains weak for women's jeans.
+
+In summary, the results suggest that pocket area is not a significant predictor of price for either men's or women's jeans in the dataset analyzed.
+Other factors not considered in this analysis are likely to have a greater influence on the pricing of jeans for both genders.
 

### 2024-04-24 paper/paper.tex
update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Jean Pockets and Gender},
  pdfauthor={Hari Lee Robledo},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Jean Pockets and Gender\thanks{Code and data are available at:
https://github.com/hari-lr/pockets-and-gender}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{subtitle}
\author{Hari Lee Robledo}
\date{April 23, 2024}

\begin{document}
\maketitle
\begin{abstract}
Fashion has long reflected and reinforced gender inequalities, with
women's clothing often lacking functional pockets found in men's
garments. A 2018 study by Jan Diehm \& Amber Thomas on The Pudding
revealed this discrepancy, highlighting inferior pocket functionality in
women's jeans. This paper aims to reproduce these findings and explore
if gender disparities extend to pricing. Using the same data, we analyze
the correlation between prices of men's and women's jeans. Results
suggest that women's jeans not only have smaller pockets but also tend
to be more expensive. This study sheds light on gender inequalities in
everyday products and their broader implications. {[}UPDATE according to
findingsThe findings revealed that pocket area alone may not be a strong
predictor of jeans prices for either gender, and there may be other
factors influencing the pricing of jeans.{]}
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, breakable]}{\end{tcolorbox}}\fi

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Throughout history, women have faced numerous restrictions and
limitations, often ingrained within societal norms and cultural
practices. Among these limitations, the realm of fashion has served as
both a reflection and an enforcer of gender-based inequalities. From
ancient times to the modern era, clothing has been a means of expressing
social status, cultural identity, and gender roles. According to design
expert, Hannah Carlson, pocket inequality stems from the way clothes are
designed and made, she explains that: ``From a very early age, I think
we sort of agree as a culture that womenswear, girlswear is meant to be
pretty,'' she said. ``And menswear, boyswear is meant to be
utilitarian'' (Alwahaidi 2018). Men's garments historically incorporated
functional pockets, allowing them to carry essentials such as money,
keys, and tools, women's clothing has often lacked this practical
feature. Instead, women's garments have frequently been designed with
form-fitting silhouettes, delicate fabrics, and ornamental details,
prioritizing aesthetics over utility.However, the 1880s, women began to
be vocal about pocket inequality, as the ``demand for the vote and the
demand for pockets were made together'' (Alwahaidi 2018).

In 2018, Jan Diehm \& Amber Thomas published Womens´s Pockets are
Inferior on \emph{The Pudding}, a data-centric digital publication. In
this paper, they ``measured pockets in both men´s and women's pants in
20 of the US' most popular blue jeans brands'' (Jan Diehm 2018). They
``programmatically determined whether various everyday items could fit
in an otherwise empty pocket in jeans that aren't being worn'' (Jan
Diehm 2018)., and concluded that women´s pockets were less functional
than men´s.

Using the data from the previously described article, this paper will
graphically reproduce the results and examine whether there is a
correlation between the prices of men's jeans and women's jeans. The
study seeks to determine if women's jeans not only have smaller and less
functional pockets but also tend to be more expensive. This will help
better understand if gender inequality is only reflected in the jean's
pockets or in pricing as well. A linear regression analysis revealed
divergent findings regarding the relationship between pocket area and
price in men's and women's jeans. For men's jeans, no significant
correlation was found between pocket area and price, indicating that
changes in pocket size do not significantly affect the price of men's
jeans. In contrast, although a negative correlation was observed in
women's jeans, it was not statistically significant, suggesting that
while larger pocket areas might be associated with slightly lower
prices, other factors likely play a more influential role in determining
the price of women's jeans.

This paper is structured into the following sections: Data, which
explains the collection and cleaning process; Results, presenting trends
and correlations found in the data; Discussion, comparing and evaluating
the data; and Conclusion, summarizing the findings.

\hypertarget{data}{%
\section{Data}\label{data}}

The data utilized in this paper was retrieved from The Pudding GitHub
Site Portal, specifically the data collected by Jan Diehm and Amber
Thomas (Jan Diehm 2018). Data was collected, cleaned, and analyzed using
the open-source statistical programming software R (R Core Team 2023).
This process involved various packages within R, including
\texttt{tidyverse} (Wickham et al. 2019), \texttt{jsonlite} (Ooms 2014),
\texttt{readr} (Wickham, Hester, and Bryan 2024), \texttt{janitor}
(Firke 2021), \texttt{dplyr} (Wickham et al. 2023), \texttt{tibble}
(Müller and Wickham 2023), \texttt{ggplot2} (Wickham 2016),
\texttt{knitr} (Xie 2024), and \texttt{kableExtra} (Zhu 2021). A
comprehensive description of the data gathering and cleaning process is
provided in the following subsections.

\hypertarget{dataset}{%
\subsection{Dataset}\label{dataset}}

In the original study, researchers examined jean pocket sizes across 20
brands, encompassing both men's and women's jeans, including skinny and
straight styles. The assessment involved scrutinizing four pairs of
jeans per brand, all tailored with a 32-inch waistband, despite falling
below the median waist size for women in the US. Measurements were
meticulously taken in physical stores located in Nashville, New York,
and Seattle, with pocket dimensions recorded while jeans were unbuttoned
and unzipped, from the inside (Jan Diehm 2018). The study incorporated
computer-generated images to illustrate pocket curvature. Various
objects, such as standard pen sizes and a front pocket wallet, were
utilized to evaluate pocket compatibility. Additionally, area
measurements were computed using the \texttt{d3.polygonArea()} function
in d3.v4, offering valuable insights into the spatial characteristics of
the jean pockets. These methods were intended to give a complete
understanding of jean pocket sizes and how well they can hold everyday
items. (Jan Diehm 2018).

In this paper, the dataset used for analysis was obtained from
\texttt{measurementRectangles.json}. This dataset mirrors the
measurements found in \texttt{measurements.csv}, including brand, style,
gender specification (men or women), product name, brand size, waist
size, fabric composition, price, and height and width measurements of
jean pockets (see Table~\ref{tbl-raw_data}). Notably, the dataset
contains a ``pocketArea'' column representing the area of the polygon
generated from a pocket's measurements. However, it's important to note
that the units of measurement for this area are not explicitly specified
in the provided metadata. To determine the units, one must examine how
the measurements were collected and processed. Since the measurements
were processed using computer-generated calculations and intended for
web display, it is possible that the pocket area is denoted in square
centimeters (px²). However, without explicit confirmation from the data
documentation or creators of the dataset, absolute certainty regarding
the units of measurement remains elusive.

\hypertarget{tbl-raw_data}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0971}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1068}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1650}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.3883}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0680}}@{}}
\caption{\label{tbl-raw_data}Sample of Raw Jean Pockets
Data}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Brand
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Style
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Men/Women
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Fabric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Price
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Brand
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Style
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Men/Women
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Fabric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Price
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
7 for All Mankind & straight & men & The Straight & 98\% cotton, 2\%
spandex & 179.00 \\
7 for All Mankind & skinny & men & Paxtyn & 92\% cotton, 6\% polyester,
2\% spandex & 209.00 \\
Abercrombie & slim & men & Langdon Slim & 95\% cotton, 4\% polyester,
1\% elastane & 78.00 \\
Abercrombie & straight & men & Kennan Straight & 95\% cotton, 4\%
polyester, 1\% elastane & 78.00 \\
American Eagle & straight & men & Straight & 85\% cotton, 13\%
polyester, 2\% elastane & 49.95 \\
\end{longtable}

\hypertarget{data-cleaning}{%
\subsection{Data Cleaning}\label{data-cleaning}}

Initially, the code read the JSON data containing pocket area
measurements, standardized the column names using the
\texttt{clean\_names()} function, and stored the cleaned data in the
\texttt{cleaned\_area\_data} dataframe. Subsequently, the data was
filtered based on gender, separating jeans intended for women and men
using the \texttt{filter()} function. Only the ``price'' and
``pocket\_area'' columns were retained for further analysis in the
resulting dataframes \texttt{men\_jeans\_data} and
\texttt{women\_jeans\_data} (see Table~\ref{tbl-menwomen_table}),
respectively. In the final step, the cleaned data was saved into CSV
files. The \texttt{write.csv()} function was utilized to export the
data, with separate CSV files generated for women's and men's jeans.

\begin{table}

\caption{\label{tbl-menwomen_table}Sample of Cleaned
Men\textquotesingle s and Women´s
Data}\begin{minipage}[t]{0.50\linewidth}
\subcaption{\label{tbl-menwomen_table-1}Men's Data}

{\centering

\begin{tabular}[t]{rr}
\toprule
Price & Pocket Area\\
\midrule
179.00 & 11222.73\\
209.00 & 10841.94\\
78.00 & 10624.65\\
78.00 & 10134.15\\
49.95 & 10555.40\\
\bottomrule
\end{tabular}

}

\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}
\subcaption{\label{tbl-menwomen_table-2}Women's Data}

{\centering

\begin{tabular}[t]{rr}
\toprule
Price & Pocket Area\\
\midrule
199.00 & 5557.218\\
159.00 & 5811.112\\
78.00 & 8757.578\\
88.00 & 9688.483\\
39.95 & 6408.587\\
\bottomrule
\end{tabular}

}

\end{minipage}%

\end{table}

To visually explore the relationship between pocket area and price for
both men's (see Figure~\ref{fig-price_per_pocket_men}) and women's jeans
(see Figure~\ref{fig-price_per_pocket_women}), scatter plots with
regression lines were created.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-price_per_pocket_men-1.pdf}

}

\caption{\label{fig-price_per_pocket_men}Jean Price vs Pocket Size
(Men)}

\end{figure}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-price_per_pocket_women-1.pdf}

}

\caption{\label{fig-price_per_pocket_women}Jean Price vs Pocket Size
(Women)}

\end{figure}

These plots visually depict the relationship between pocket area and
price for men's and women's jeans. Additionally, to compute the standard
deviation of price for both men's and women's jeans, the \texttt{sd()}
function can be applied to the respective columns in the
\texttt{men\_jeans\_data} and \texttt{women\_jeans\_data} dataframes.
The standard deviation of price for women's jeans is 48.79, while for
men's jeans, it is 40.49, indicating the variability in prices within
each gender category. This measure helps assess the spread of prices
around the mean and provides insight into the degree of dispersion in
price values among the observed jeans.

\hypertarget{model}{%
\section{Model}\label{model}}

To gain further insights and make predictions about {[}{]}, we will be
implementing a linear regression model.

The final model is displayed here.

\[L = \beta_0 + \beta_1S + \epsilon\]

Where:

\begin{itemize}
\tightlist
\item
  \(L\) represents the dependent variable, which is the overall price of
  jeans
\item
  \(S\) represents the independent variable, which is the pocket area
\item
  \(\beta_0\) represents the intercept of the regression line, which is
  the predicted value of \(L\) when \(S\) is equal to zero
\item
  \(\beta_1\) represents the slope of the regression line, which is the
  change in \(L\) for a one-unit increase in \(S\)
\item
  \(\epsilon\) represents the random error term, which accounts for
  variability in \(L\) that is not explained by the relationship with
  \(S\)
\end{itemize}

Linear regression seeks to determine the optimal parameters \(\beta_0\)
and \(\beta_1\) that minimize the discrepancies between predicted and
observed prices across varying pocket areas in the dataset. Through this
minimization process, the model constructs a line that most accurately
represents the association between pocket area and price. Consequently,
we can predict price values based on known pocket area measurements.
This regression analysis sheds light on how pocket area influences the
pricing of jeans for both men and women, offering valuable insights into
the pricing dynamics within each gender category.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{tbl-men_model_summary}{}
\begin{table}

\caption{\label{tbl-men_model_summary}Summary of Linear Regression Model for Men's Jeans }Summary of Linear Regression Model for Men's Jeans}
\centering
\begin{tabular}[t]{l|c|c|c|c}
\hline
  & Estimate & Std. Error & t value & Pr(>|t|)\\
\hline
(Intercept) & 105.9002168 & 53.5254438 & 1.9785024 & 0.0551543\\
\hline
pocket\_area & -0.0022856 & 0.0049134 & -0.4651738 & 0.6444619\\
\hline
\end{tabular}
\end{table}

\hypertarget{tbl-women_model_summary}{}
\begin{table}

\caption{\label{tbl-women_model_summary}Summary of Linear Regression Model for Women's Jeans }Summary of Linear Regression Model for Women's Jeans}
\centering
\begin{tabular}[t]{l|c|c|c|c}
\hline
  & Estimate & Std. Error & t value & Pr(>|t|)\\
\hline
(Intercept) & 136.7159600 & 42.0324855 & 3.252626 & 0.0024018\\
\hline
pocket\_area & -0.0093445 & 0.0068483 & -1.364495 & 0.1804384\\
\hline
\end{tabular}
\end{table}

A scatterplot was generated to compare pocket area and price for both
men's and women's jeans. Each gender category was represented by a
distinct color in the plot. Additionally, linear regression lines were
overlaid for each gender group to observe potential differences in the
relationship between pocket area and price.

This visualization facilitated the comparison of how pocket area related
to price for men's and women's jeans separately. By including separate
regression lines for each gender, we could assess the direction and
strength of the relationship between these variables within each group.
The use of different colors for men and women aided in distinguishing
between the two groups, enabling easy interpretation of the plot.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-price_per_pocket_gender-1.pdf}

}

\caption{\label{fig-price_per_pocket_gender}Jean Price vs.~Pocket Area
Size per Gender}

\end{figure}

After visualizing the linear regression for both men's and women's
jeans, I proceeded to analyze the results obtained from the regression
models:

The linear regression models for both men's and women's jeans revealed
interesting insights into the relationship between pocket area and
price.

For men's jeans, the coefficient estimate for pocket area (\(\beta_1\))
is -0.002286, indicating a very small and statistically insignificant
negative association between pocket area and price. This suggests that,
on average, changes in pocket area do not have a significant impact on
the price of men's jeans. The p-value associated with the pocket area
coefficient is 0.6445, which is much greater than the typical
significance level of 0.05. Additionally, the ( R\^{}2 ) value, which
measures the proportion of variance in the dependent variable explained
by the independent variable, is very low at 0.005662. Overall, these
results suggest that there is little evidence to suggest a meaningful
relationship between pocket area and price for men's jeans.

In contrast, for women's jeans, the coefficient estimate for pocket area
is -0.009345, also indicating a small negative association with price,
although it is slightly larger in magnitude compared to men's jeans.
However, like men's jeans, this coefficient is statistically
insignificant with a p-value of 0.1804. The ( R\^{}2 ) value for women's
jeans is slightly higher at 0.04671, indicating that pocket area
explains a slightly larger proportion of the variance in price compared
to men's jeans. Despite this, the overall relationship between pocket
area and price remains weak for women's jeans.

In summary, the results suggest that pocket area is not a significant
predictor of price for either men's or women's jeans in the dataset
analyzed. Other factors not considered in this analysis are likely to
have a greater influence on the pricing of jeans for both genders.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{sec-first-point}{%
\subsection{First discussion point}\label{sec-first-point}}

\hypertarget{second-discussion-point}{%
\subsection{Second discussion point}\label{second-discussion-point}}

\hypertarget{third-discussion-point}{%
\subsection{Third discussion point}\label{third-discussion-point}}

\#\#Weaknesses and next steps

\newpage

\appendix

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-carlson}{}}%
Alwahaidi, Keena. 2018. \emph{Women's Apparel Doesn't Have Enough
Pockets. This Expert Says That Has to Change}.

\leavevmode\vadjust pre{\hypertarget{ref-janitor}{}}%
Firke, Sam. 2021. \emph{Janitor: Simple Tools for Examining and Cleaning
Dirty Data}. \url{https://github.com/sfirke/janitor}.

\leavevmode\vadjust pre{\hypertarget{ref-pudding}{}}%
Jan Diehm, Amber Thomas. 2018. \emph{Womens´s Pockets Are Inferior}.

\leavevmode\vadjust pre{\hypertarget{ref-tibble}{}}%
Müller, Kirill, and Hadley Wickham. 2023. \emph{Tibble: Simple Data
Frames}. \url{https://tibble.tidyverse.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-jsonlite}{}}%
Ooms, Jeroen. 2014. {``The Jsonlite Package: A Practical and Consistent
Mapping Between JSON Data and r Objects.''} \emph{arXiv:1403.2805
{[}Stat.CO{]}}. \url{https://arxiv.org/abs/1403.2805}.

\leavevmode\vadjust pre{\hypertarget{ref-citeR}{}}%
R Core Team. 2023. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
Analysis}. Springer-Verlag New York.
\url{https://ggplot2.tidyverse.org}.

\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis
Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.

\leavevmode\vadjust pre{\hypertarget{ref-readr}{}}%
Wickham, Hadley, Jim Hester, and Jennifer Bryan. 2024. \emph{Readr: Read
Rectangular Text Data}. \url{https://readr.tidyverse.org}.

\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
Xie, Yihui. 2024. \emph{Knitr: A General-Purpose Package for Dynamic
Report Generation in r}. \url{https://yihui.org/knitr/}.

\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
Zhu, Hao. 2021. \emph{kableExtra: Construct Complex Table with 'Kable'
and Pipe Syntax}.

\end{CSLReferences}

\end{document}

### 2024-04-24 paper/paper.tex
update

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, enhanced, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi
 

### 2024-04-24 paper/paper.qmd
update

@@
 However, without explicit confirmation from the data documentation or creators of the dataset, absolute certainty regarding the units of measurement remains elusive.
+\newpage
 
@@
 
+\newpage
 ```{r}
@@
 ```
+\newpage
 
-To visually explore the relationship between pocket area and price for both men's (see @fig-price_per_pocket_men) and women's jeans (see @fig-price_per_pocket_women), scatter plots with regression lines were created.
+To visually explore the relationship between pocket area and price for both men's and women's jeans scatter plots with regression lines were created (see Figure 1 and 2).
 
@@
 #| echo: false
-#| label: fig-price_per_pocket_men
-#| fig-cap: "Jean Price vs Pocket Size (Men)"
+#| label: fig-price_pocket
+#| layout-ncol: 2
+#| fig-cap: "Jean Price vs Pocket Size"
 
@@
   labs(
-    title = "Pocket Area and Price for Men's Jeans",
+    title = "Pocket Size and Price for Men's Jeans",
     x = "Pocket Area",
@@
 
-```
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: fig-price_per_pocket_women
-#| fig-cap: "Jean Price vs Pocket Size (Women)"
-
 # Create plot for men_jeans_data
@@
   labs(
-    title = "Pocket Area and Price for Women's Jeans",
+    title = "Pocket Size and Price for Women's Jeans",
     x = "Pocket Area",
@@
 women_price_sd <- sd(women_jeans_data$price)
+
 ```
@@
 
+\newpage
+
 # Model
-To gain further insights and make predictions about [], we will be implementing a linear regression model.
+To gain further insights and make predictions about jeans pricing,  a linear regression model was implemented.
 
@@
 
-Linear regression seeks to determine the optimal parameters $\beta_0$ and $\beta_1$ that minimize the discrepancies between predicted and observed prices across varying pocket areas in the dataset.
+The linear regression seeked to determine the optimal parameters $\beta_0$ and $\beta_1$ that minimize the discrepancies between predicted and observed prices across varying pocket areas in the dataset.
 Through this minimization process, the model constructs a line that most accurately represents the association between pocket area and price.
@@
 
+\newpage
 # Results
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-men_model_summary
-#| tbl-cap: "Summary of Linear Regression Model for Men's Jeans"
-# Fit a linear regression model for men's jeans
-men_model <- lm(price ~ pocket_area, data = men_jeans_data)
-
-# View the summary of the model
-summary_men <- summary(men_model)
-summary_table_men <- summary_men$coefficients
-
-# Print the summary table
-kable(summary_table_men, caption = "Summary of Linear Regression Model for Men's Jeans", align = "c")
-
-```
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-women_model_summary
-#| tbl-cap: "Summary of Linear Regression Model for Women's Jeans"
-# Fit a linear regression model for women's jeans
-women_model <- lm(price ~ pocket_area, data = women_jeans_data)
-
-# View the summary of the model
-summary_women <- summary(women_model)
-summary_table_women <- summary_women$coefficients
-
-# Print the summary table
-kable(summary_table_women, caption = "Summary of Linear Regression Model for Women's Jeans", align = "c")
-```
-
-A scatterplot was generated to compare pocket area and price for both men's and women's jeans.
+A merged scatterplot was generated to compare pocket area and price for both men's and women's jeans.
 Each gender category was represented by a distinct color in the plot.
-Additionally, linear regression lines were overlaid for each gender group to observe potential differences in the relationship between pocket area and price.
+Additionally, linear regression lines were overlaid for each gender group to observe potential differences in the relationship between pocket area and price (see @fig-price_per_pocket_gender).
 
@@
 The use of different colors for men and women aided in distinguishing between the two groups, enabling easy interpretation of the plot.
+
 ```{r}
@@
 #| label: fig-price_per_pocket_gender
-#| fig-cap: "Jean Price vs. Pocket Area Size per Gender"
+#| fig-cap: "Jean Price vs. Pocket Size per Gender"
 
@@
   labs(
-    title = "Pocket Area and Price by Gender",
-    x = "Pocket Area (square pixels)",
+    title = "Pocket Size and Price by Gender",
+    x = "Pocket Area",
     y = "Price",
@@
 
-After visualizing the linear regression for both men's and women's jeans, I proceeded to analyze the results obtained from the regression models:
-
-The linear regression models for both men's and women's jeans revealed interesting insights into the relationship between pocket area and price.
+After visualizing the linear regression for both men's and women's jeans, the results obtained from the regression models were analyzed.
 
@@
 Additionally, the \( R^2 \) value, which measures the proportion of variance in the dependent variable explained by the independent variable, is very low at 0.005662.
-Overall, these results suggest that there is little evidence to suggest a meaningful relationship between pocket area and price for men's jeans.
+Overall, these results suggest that there is little evidence to suggest a meaningful relationship between pocket area and price for men's jeans (see @tbl-men_lm).
 
@@
 The \( R^2 \) value for women's jeans is slightly higher at 0.04671, indicating that pocket area explains a slightly larger proportion of the variance in price compared to men's jeans.
-Despite this, the overall relationship between pocket area and price remains weak for women's jeans.
+Despite this, the overall relationship between pocket area and price remains weak for women's jeans (see @tbl-women_lm).
 
@@
 Other factors not considered in this analysis are likely to have a greater influence on the pricing of jeans for both genders.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-men_lm
+#| tbl-cap: "Summary of Linear Regression Model for Men's Jeans"
+
+# Fit a linear regression model for men's jeans
+men_model <- lm(price ~ pocket_area, data = men_jeans_data)
+
+# View the summary of the model
+summary_men <- summary(men_model)
+summary_table_men <- summary_men$coefficients
+
+# Print the summary table
+kable(summary_table_men, align = "c")
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-women_lm
+#| tbl-cap: "Summary of Linear Regression Model for Women's Jeans"
+# Fit a linear regression model for women's jeans
+women_model <- lm(price ~ pocket_area, data = women_jeans_data)
+
+# View the summary of the model
+summary_women <- summary(women_model)
+summary_table_women <- summary_women$coefficients
+
+# Print the summary table
+kable(summary_table_women, align = "c")
+```
 
@@
 
-\appendix
-
-# Appendix {-}
-
-\newpage
-
 # References

### 2024-04-24 scripts/02-data_cleaning.qmd
update

@@
 
-# Select the rows of interest
-cleaned_area_data <-
-  cleaned_area_data |>
+# Filter the data to include only jeans for women and select columns
+women_jeans_data <- cleaned_area_data |>
+  filter(men_women == "women") |>
   select(
-    brand,
-    men_women,
     price,
-    pocket_area,
+    pocket_area
   )
 
-cleaned_area_data
+women_jeans_data
 
+# Filter the data to include only jeans for men and select columns
+men_jeans_data <- cleaned_area_data|>
+  filter(men_women == "men") |>
+  select(
+    price,
+    pocket_area
+  )
+
+men_jeans_data
 ```
@@
 #### Save cleaned data ####
-# save json cleaned data (pocket area measurements)
+# Code referenced from: chat.openai.com
 
@@
 
-# Write the cleaned data frame to a CSV file
-write_csv(cleaned_area_data, csv_file)
+# Specify file paths
+men_csv_file <- here::here("data/analysis_data/men_jeans_data.csv")
+women_csv_file <- here::here("data/analysis_data/women_jeans_data.csv")
+
+# Save men_jeans_data to a CSV file
+write.csv(men_jeans_data, men_csv_file, row.names = FALSE)
+
+# Save women_jeans_data to a CSV file
+write.csv(women_jeans_data, women_csv_file, row.names = FALSE)
+
 ```

### 2024-04-24 paper/paper.qmd
update

@@
 Men's garments historically incorporated functional pockets, allowing them to carry essentials such as money, keys, and tools, women's clothing has often lacked this practical feature.
-Instead, women's garments have frequently been designed with form-fitting silhouettes, delicate fabrics, and ornamental details, prioritizing aesthetics over utility.However, the 1880s, women began to be vocal about pocket inequality, as the "demand for the vote and the demand for pockets were made together" [@carlson].
+Instead, women's garments have frequently been designed with form-fitting silhouettes, delicate fabrics, and ornamental details, prioritizing aesthetics over utility.
+However, the 1880s, women began to be vocal about pocket inequality, as the "demand for the vote and the demand for pockets were made together" [@carlson].
 
@@
 
-\newpage
 # Results
@@
 Other factors not considered in this analysis are likely to have a greater influence on the pricing of jeans for both genders.
+\newpage
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
+
+as mentioned before
+
 ## Second discussion point
 ## Third discussion point
+https://www.mydoh.ca/learn/blog/lifestyle/what-is-the-pink-tax-a-guide-for-teens/
 
-##Weaknesses and next steps
+## Weaknesses and next steps
+
+The analysis has several limitations.
+Firstly, it narrowly focuses on the relationship between pocket area and price, neglecting other potential pricing determinants in the fashion industry.
+The dataset's limited scope, derived from measurements of specific brands and styles, may not be representative of the broader jeans market.
+Additionally, the regression analysis yielded statistically insignificant results for pocket area coefficients in both men's and women's jeans, indicating a weak relationship.
+Moreover, the unknown units of pocket area measurement limits accurate interpretation.
+
+To address these limitations, future research could incorporate additional pricing determinants like brand reputation and market demand.
+Diversifying the dataset to include jeans from additional brands and price points would enhance representativeness.
+Qualitative research methods could provide deeper insights into consumer behavior, offering a more comprehensive understanding of purchasing decisions beyond pocket considerations.
+Considering cultural and societal factors influencing fashion trends would offer valuable context for interpreting the results.
+Moreover, it would be important to increment the number of jeans measured to improve the robustness and generalizability of the findings.
 

### 2024-04-24 paper/paper.tex
update

@@
 \author{Hari Lee Robledo}
-\date{April 23, 2024}
+\date{April 24, 2024}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, enhanced, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, frame hidden, breakable, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 
@@
 form-fitting silhouettes, delicate fabrics, and ornamental details,
-prioritizing aesthetics over utility.However, the 1880s, women began to
+prioritizing aesthetics over utility. However, the 1880s, women began to
 be vocal about pocket inequality, as the ``demand for the vote and the
@@
 documentation or creators of the dataset, absolute certainty regarding
-the units of measurement remains elusive.
+the units of measurement remains elusive. \newpage
 
@@
 
+\newpage
+
 \begin{table}
@@
 
+\newpage
+
 To visually explore the relationship between pocket area and price for
-both men's (see Figure~\ref{fig-price_per_pocket_men}) and women's jeans
-(see Figure~\ref{fig-price_per_pocket_women}), scatter plots with
-regression lines were created.
+both men's and women's jeans scatter plots with regression lines were
+created (see Figure 1 and 2).
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/fig-price_per_pocket_men-1.pdf}
+\begin{minipage}[t]{0.50\linewidth}
+
+{\centering
+
+\raisebox{-\height}{
+
+\includegraphics{paper_files/figure-pdf/fig-price_pocket-1.pdf}
 
@@
 
-\caption{\label{fig-price_per_pocket_men}Jean Price vs Pocket Size
-(Men)}
-
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-price_per_pocket_women-1.pdf}
+\caption{\label{fig-price_pocket-1}Jean Price vs Pocket Size}
 
@@
 
-\caption{\label{fig-price_per_pocket_women}Jean Price vs Pocket Size
-(Women)}
+\end{minipage}%
+%
+\begin{minipage}[t]{0.50\linewidth}
+
+{\centering
+
+\raisebox{-\height}{
+
+\includegraphics{paper_files/figure-pdf/fig-price_pocket-2.pdf}
+
+}
+
+\caption{\label{fig-price_pocket-2}Jean Price vs Pocket Size}
+
+}
+
+\end{minipage}%
 
@@
 
+\newpage
+
 \hypertarget{model}{%
@@
 
-To gain further insights and make predictions about {[}{]}, we will be
-implementing a linear regression model.
+To gain further insights and make predictions about jeans pricing, a
+linear regression model was implemented.
 
@@
 
-Linear regression seeks to determine the optimal parameters \(\beta_0\)
-and \(\beta_1\) that minimize the discrepancies between predicted and
-observed prices across varying pocket areas in the dataset. Through this
-minimization process, the model constructs a line that most accurately
-represents the association between pocket area and price. Consequently,
-we can predict price values based on known pocket area measurements.
-This regression analysis sheds light on how pocket area influences the
-pricing of jeans for both men and women, offering valuable insights into
-the pricing dynamics within each gender category.
+The linear regression seeked to determine the optimal parameters
+\(\beta_0\) and \(\beta_1\) that minimize the discrepancies between
+predicted and observed prices across varying pocket areas in the
+dataset. Through this minimization process, the model constructs a line
+that most accurately represents the association between pocket area and
+price. Consequently, we can predict price values based on known pocket
+area measurements. This regression analysis sheds light on how pocket
+area influences the pricing of jeans for both men and women, offering
+valuable insights into the pricing dynamics within each gender category.
 
@@
 
-\hypertarget{tbl-men_model_summary}{}
-\begin{table}
-
-\caption{\label{tbl-men_model_summary}Summary of Linear Regression Model for Men's Jeans }Summary of Linear Regression Model for Men's Jeans}
-\centering
-\begin{tabular}[t]{l|c|c|c|c}
-\hline
-  & Estimate & Std. Error & t value & Pr(>|t|)\\
-\hline
-(Intercept) & 105.9002168 & 53.5254438 & 1.9785024 & 0.0551543\\
-\hline
-pocket\_area & -0.0022856 & 0.0049134 & -0.4651738 & 0.6444619\\
-\hline
-\end{tabular}
-\end{table}
-
-\hypertarget{tbl-women_model_summary}{}
-\begin{table}
-
-\caption{\label{tbl-women_model_summary}Summary of Linear Regression Model for Women's Jeans }Summary of Linear Regression Model for Women's Jeans}
-\centering
-\begin{tabular}[t]{l|c|c|c|c}
-\hline
-  & Estimate & Std. Error & t value & Pr(>|t|)\\
-\hline
-(Intercept) & 136.7159600 & 42.0324855 & 3.252626 & 0.0024018\\
-\hline
-pocket\_area & -0.0093445 & 0.0068483 & -1.364495 & 0.1804384\\
-\hline
-\end{tabular}
-\end{table}
-
-A scatterplot was generated to compare pocket area and price for both
-men's and women's jeans. Each gender category was represented by a
+A merged scatterplot was generated to compare pocket area and price for
+both men's and women's jeans. Each gender category was represented by a
 distinct color in the plot. Additionally, linear regression lines were
 overlaid for each gender group to observe potential differences in the
-relationship between pocket area and price.
+relationship between pocket area and price (see
+Figure~\ref{fig-price_per_pocket_gender}).
 
@@
 
-\caption{\label{fig-price_per_pocket_gender}Jean Price vs.~Pocket Area
-Size per Gender}
+\caption{\label{fig-price_per_pocket_gender}Jean Price vs.~Pocket Size
+per Gender}
 
@@
 After visualizing the linear regression for both men's and women's
-jeans, I proceeded to analyze the results obtained from the regression
-models:
-
-The linear regression models for both men's and women's jeans revealed
-interesting insights into the relationship between pocket area and
-price.
+jeans, the results obtained from the regression models were analyzed.
 
@@
 results suggest that there is little evidence to suggest a meaningful
-relationship between pocket area and price for men's jeans.
+relationship between pocket area and price for men's jeans (see
+Table~\ref{tbl-men_lm}).
 
@@
 to men's jeans. Despite this, the overall relationship between pocket
-area and price remains weak for women's jeans.
+area and price remains weak for women's jeans (see
+Table~\ref{tbl-women_lm}).
 
@@
 have a greater influence on the pricing of jeans for both genders.
+\newpage
+
+\hypertarget{tbl-men_lm}{}
+\begin{table}
+\caption{\label{tbl-men_lm}Summary of Linear Regression Model for Men's Jeans }\tabularnewline
+
+\centering
+\begin{tabular}{l|c|c|c|c}
+\hline
+  & Estimate & Std. Error & t value & Pr(>|t|)\\
+\hline
+(Intercept) & 105.9002168 & 53.5254438 & 1.9785024 & 0.0551543\\
+\hline
+pocket\_area & -0.0022856 & 0.0049134 & -0.4651738 & 0.6444619\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{tbl-women_lm}{}
+\begin{table}
+\caption{\label{tbl-women_lm}Summary of Linear Regression Model for Women's Jeans }\tabularnewline
+
+\centering
+\begin{tabular}{l|c|c|c|c}
+\hline
+  & Estimate & Std. Error & t value & Pr(>|t|)\\
+\hline
+(Intercept) & 136.7159600 & 42.0324855 & 3.252626 & 0.0024018\\
+\hline
+pocket\_area & -0.0093445 & 0.0068483 & -1.364495 & 0.1804384\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-\hypertarget{sec-first-point}{%
-\subsection{First discussion point}\label{sec-first-point}}
+\hypertarget{first-discussion-point}{%
+\subsection{First discussion point}\label{first-discussion-point}}
+
+as mentioned before
 
@@
 
-\#\#Weaknesses and next steps
+https://www.mydoh.ca/learn/blog/lifestyle/what-is-the-pink-tax-a-guide-for-teens/
 
-\newpage
+\hypertarget{weaknesses-and-next-steps}{%
+\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}}
 
-\appendix
+The analysis has several limitations. Firstly, it narrowly focuses on
+the relationship between pocket area and price, neglecting other
+potential pricing determinants in the fashion industry. The dataset's
+limited scope, derived from measurements of specific brands and styles,
+may not be representative of the broader jeans market. Additionally, the
+regression analysis yielded statistically insignificant results for
+pocket area coefficients in both men's and women's jeans, indicating a
+weak relationship. Moreover, the unknown units of pocket area
+measurement limits accurate interpretation.
 
-\hypertarget{appendix}{%
-\section*{Appendix}\label{appendix}}
-\addcontentsline{toc}{section}{Appendix}
+To address these limitations, future research could incorporate
+additional pricing determinants like brand reputation and market demand.
+Diversifying the dataset to include jeans from additional brands and
+price points would enhance representativeness. Qualitative research
+methods could provide deeper insights into consumer behavior, offering a
+more comprehensive understanding of purchasing decisions beyond pocket
+considerations. Considering cultural and societal factors influencing
+fashion trends would offer valuable context for interpreting the
+results. Moreover, it would be important to increment the number of
+jeans measured to improve the robustness and generalizability of the
+findings.
 

### 2024-04-24 scripts/00-simulate_data.R
update readme and scripts

@@ -1,0 +1,63 @@
+#### Preamble ####
+# Purpose: Simulate the data set from the Pockets paper by Jan Diehm & Amber Thomas. 
+# Author: Hari Lee Robledo
+# Date: April 2 2023 
+# Contact: hari.leerobledo@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: None
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Simulate data ####
+# Code referenced from: https://chat.openai.com/
+
+# Set seed for reproducibility
+set.seed(123)
+
+# Number of jeans for each gender
+num_jeans <- 40
+
+# Generate data for men's jeans
+men_jeans <- data.frame(
+  gender = rep("Men", num_jeans),
+  price = round(runif(num_jeans, min = 30, max = 200), 2), 
+  pocket_area = round(runif(num_jeans, min = 12, max = 20), 2) 
+)
+
+# Generate data for women's jeans
+women_jeans <- data.frame(
+  gender = rep("Women", num_jeans),
+  price = round(runif(num_jeans, min = 30, max = 200), 2), 
+  pocket_area = round(runif(num_jeans, min = 12, max = 20), 2) 
+)
+# Combine the datasets
+jeans_data <- rbind(men_jeans, women_jeans)
+
+jeans_data
+
+
+#### Test simulated data ####
+# Code referenced from: https://chat.openai.com/
+
+# Test 1: Check total number of rows
+if (nrow(jeans_data) == 80) {
+  print("Test 1 Passed: Total number of rows is correct.")
+} else {
+  print("Test 1 Failed: Total number of rows is incorrect.")
+}
+
+# Test 2: Check price range
+if (all(jeans_data$price >= 30) & all(jeans_data$price <= 200)) {
+  print("Test 2 Passed: Price range is correct.")
+} else {
+  print("Test 2 Failed: Price range is incorrect.")
+}
+
+# Test 3: Check pocket area range
+if (all(jeans_data$pocket_area >= 12) & all(jeans_data$pocket_area <= 20)) {
+  print("Test 3 Passed: Pocket area range is correct.")
+} else {
+  print("Test 3 Failed: Pocket area range is incorrect.")
+}

### 2024-04-24 scripts/01-download_data.R

@@ -6,24 +6,22 @@
 # License: MIT
 # Pre-requisites: None
 
-```{r}
 #### Workspace setup ####
 #install.packages()
 library(tidyverse)
 library(readr)
 library(jsonlite)
-```
 
-``` {r}
+
 #### Download measurements json data ####
 # Code referenced from:chat.openai.com 
 github_url <- "https://raw.githubusercontent.com/the-pudding/data/master/pockets/measurementRectangles.json"
 
 # Read the JSON data from GitHub into R
 pocket_area_data <- fromJSON(github_url)
-```
 
-```{r}
+
+
 #### Save measurements json data ####
 # Code referenced from: chat.openai.com
 json_string <- toJSON(pocket_area_data, pretty = TRUE)
@@ -40,5 +38,5 @@ df <- as.data.frame(pocket_area_data)
 
 # Save data frame as CSV
 write.csv(df, "data/raw_data/pocket_area_data.csv", row.names = FALSE)
-```
+
 

### 2024-04-24 scripts/02-data_cleaning.R

@@ -6,16 +6,14 @@
 # License: MIT
 # Pre-requisites: 01-download_data.R
 
-```{r}
+
 #### Workspace setup ####
 library(tidyverse)
 library(jsonlite)
 library(readr)
 library(janitor)
 library(dplyr)
-```
 
-```{r}
 #### Clean data ####
 
 # Code referenced from: chat.openai.com 
@@ -50,9 +48,7 @@ men_jeans_data <- cleaned_area_data|>
   )
 
 men_jeans_data
-```
 
-```{r}
 #### Save cleaned data ####
 # Code referenced from: chat.openai.com 
 
@@ -69,5 +65,5 @@ write.csv(men_jeans_data, men_csv_file, row.names = FALSE)
 # Save women_jeans_data to a CSV file
 write.csv(women_jeans_data, women_csv_file, row.names = FALSE)
 
-```
+
 

### 2024-04-24 scripts/03-test_data.R

@@ -1,15 +1,46 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests data from the Womens´s Pockets are Inferior paper by Jan Diehm & Amber Thomas. 
+# Author: Hari Lee Robledo
+# Date: April 2 2023 
+# Contact: hari.leerobledo@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-data_cleaning.R
+
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####
+# Test 1
+
+# Check number of items in women_jeans_data 
+if (nrow(women_jeans_data) == 40) {
+  print("Test Passed: Number of items in women_jeans_data is correct (40).")
+} else {
+  print("Test Failed: Number of items in women_jeans_data is incorrect.")
+}
+
+# Check number of items in men_jeans_data
+if (nrow(men_jeans_data) == 40) {
+  print("Test Passed: Number of items in men_jeans_data is correct (40).")
+} else {
+  print("Test Failed: Number of items in men_jeans_data is incorrect.")
+}
+
+# Test 2
+
+# Check lowest price in men_jeans_data
+if (min(men_jeans_data$price) == 39.99) {
+  print("Test Passed: Lowest price in men_jeans_data is correct.")
+} else {
+  print("Test Failed: Lowest price in men_jeans_data is incorrect.")
+}
+
+# Check lowest price in women_jeans_data
+if (min(women_jeans_data$price) == 9.99) {
+  print("Test Passed: Lowest price in women_jeans_data is correct.")
+} else {
+  print("Test Failed: Lowest price in women_jeans_data is incorrect.")
+}

### 2024-04-24 paper/paper.qmd
update

@@
 library(kableExtra)
+library(knitr)
 
@@
 
-In this paper, the dataset used for analysis was obtained from `measurementRectangles.json`.
+For this paper, the dataset used for analysis was obtained from `measurementRectangles.json`.
 This dataset mirrors the measurements found in `measurements.csv`, including brand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data).
@@
   )
+
 ```
@@
 Other factors not considered in this analysis are likely to have a greater influence on the pricing of jeans for both genders.
-\newpage
 

### 2024-04-24 scripts/03-test_data.R

@@ -13,20 +13,22 @@ library(tidyverse)
 
 
 #### Test data ####
-# Test 1
+# Code referenced from: https://chat.openai.com/
 
-# Check number of items in women_jeans_data 
-if (nrow(women_jeans_data) == 40) {
-  print("Test Passed: Number of items in women_jeans_data is correct (40).")
-} else {
-  print("Test Failed: Number of items in women_jeans_data is incorrect.")
-}
+# Test 1
 
 # Check number of items in men_jeans_data
 if (nrow(men_jeans_data) == 40) {
   print("Test Passed: Number of items in men_jeans_data is correct (40).")
 } else {
   print("Test Failed: Number of items in men_jeans_data is incorrect.")
+}
+
+# Check number of items in women_jeans_data 
+if (nrow(women_jeans_data) == 40) {
+  print("Test Passed: Number of items in women_jeans_data is correct (40).")
+} else {
+  print("Test Failed: Number of items in women_jeans_data is incorrect.")
 }
 
 # Test 2
@@ -43,4 +45,19 @@ if (min(women_jeans_data$price) == 9.99) {
   print("Test Passed: Lowest price in women_jeans_data is correct.")
 } else {
   print("Test Failed: Lowest price in women_jeans_data is incorrect.")
+}
+
+# Test 3
+# Check highest price in men_jeans_data
+if (max(men_jeans_data$price) == 209) {
+  print("Test Passed: Highest price in men_jeans_data is correct.")
+} else {
+  print("Test Failed: Highest price in men_jeans_data is incorrect.")
+}
+
+# Check highest price in women_jeans_data
+if (max(women_jeans_data$price) == 249) {
+  print("Test Passed: Highest price in women_jeans_data is correct.")
+} else {
+  print("Test Failed: Highest price in women_jeans_data is incorrect.")
 }

### 2024-04-24 paper/paper.qmd
final paper

--- 2024-04-24 paper/paper.qmd
@@
 date-format: long
-abstract: "Fashion has long reflected and reinforced gender inequalities, with women's clothing often lacking functional pockets found in men's garments.
-A 2018 study by Jan Diehm & Amber Thomas on The Pudding revealed this discrepancy, highlighting inferior pocket functionality in women's jeans.
-This paper aims to reproduce these findings and explore if gender disparities extend to pricing.
-Using the same data, we analyze the correlation between prices of men's and women's jeans.
-Results suggest that women's jeans not only have smaller pockets but also tend to be more expensive.
-This study sheds light on gender inequalities in everyday products and their broader implications.
-[UPDATE according to findingsThe findings revealed that pocket area alone may not be a strong predictor of jeans prices for either gender, and there may be other factors influencing the pricing of jeans.]"
+abstract: "This paper explores the intersection of gender, fashion, and pricing dynamics, focusing on pocket inequality in jeans.
+The study investigates whether there is a correlation between pocket size and jean prices for men and women.
+Utilizing data collected by Diehm & Thomas (2018) from 20 popular US jeans brands, the analysis employs linear regression models, standard deviation and averages to examine the relationship between pocket area and price.
+The findings reveal that pocket area is not a significant predictor of price for either men's or women's jeans, indicating complex pricing dynamics beyond pocket considerations.
+The implications of these findings underscore the need for further discussions surrounding the pink tax and pocket inequality by providing empirical evidence of pricing disparities.
+While the average price of women's jeans appears slightly lower than men's, the considerable variability in prices within each gender category suggests deeper complexities."
 format: pdf
@@
 
-\newpage
-
 # Introduction
@@
 
-In 2018, Jan Diehm & Amber Thomas published Womens´s Pockets are Inferior on *The Pudding*, a data-centric digital publication.
+In 2018, Jan Diehm & Amber Thomas published *Womens´s Pockets are Inferior* on *The Pudding*, a data-centric digital publication.
 In this paper, they "measured pockets in both men´s and women’s pants in 20 of the US’ most popular blue jeans brands" [@pudding].
@@
 
-Using the data from the previously described article, this paper will graphically reproduce the results and examine whether there is a correlation between the prices of men's jeans and women's jeans.
+Using the data from the previously described article, this paper examines whether there is a correlation between the prices of men's jeans and women's jeans.
 The study seeks to determine if women's jeans not only have smaller and less functional pockets but also tend to be more expensive.
@@
 Measurements were meticulously taken in physical stores located in Nashville, New York, and Seattle, with pocket dimensions recorded while jeans were unbuttoned and unzipped, from the inside [@pudding].
-The study incorporated computer-generated images to illustrate pocket curvature.
+
+Additionally,the study incorporated computer-generated images to illustrate pocket curvature.
 Various objects, such as standard pen sizes and a front pocket wallet, were utilized to evaluate pocket compatibility.
-Additionally, area measurements were computed using the `d3.polygonArea()` function in d3.v4, offering valuable insights into the spatial characteristics of the jean pockets.
-These methods were intended to give a complete understanding of jean pocket sizes and how well they can hold everyday items.
-[@pudding].
+These area measurements were computed using the `d3.polygonArea()` function in d3.v4 [@pudding].
 
-In this paper, the dataset used for analysis was obtained from `measurementRectangles.json`.
-This dataset mirrors the measurements found in `measurements.csv`, including brand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data).
+For this paper, the dataset used  was obtained from `measurementRectangles.json`.
+This dataset mirrors the measurements found in `measurements.csv`, including pixelsrand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data).
 Notably, the dataset contains a "pocketArea" column representing the area of the polygon generated from a pocket's measurements.
@@
 To determine the units, one must examine how the measurements were collected and processed.
-Since the measurements were processed using computer-generated calculations and intended for web display, it is possible that the pocket area is denoted in square centimeters (px²).
+Since the measurements were processed using computer-generated calculations and intended for web display, it is possible that the pocket area is denoted in square pixels (px²).
 However, without explicit confirmation from the data documentation or creators of the dataset, absolute certainty regarding the units of measurement remains elusive.
@@
 In the final step, the cleaned data was saved into CSV files.
-The `write.csv()` function was utilized to export the data, with separate CSV files generated for women's and men's jeans.
+The `write.csv()` function was utilized to export and save the data.
 
@@
 
-# Create plot for men_jeans_data
+# Calculate the average price for men's jeans
+men_avg_price <- mean(men_jeans_data$price)
+
+# Create plot for women_jeans_data
 women_jeans_plot <- ggplot(women_jeans_data, aes(x = pocket_area, y = price)) +
@@
 
+# Calculate the average price for women's jeans
+women_avg_price <- mean(women_jeans_data$price)
+
 ```
-
-These plots visually depict the relationship between pocket area and price for men's and women's jeans.
-Additionally, to compute the standard deviation of price for both men's and women's jeans, the `sd()` function can be applied to the respective columns in the `men_jeans_data` and `women_jeans_data` dataframes.
-The standard deviation of price for women's jeans is 48.79, while for men's jeans, it is 40.49, indicating the variability in prices within each gender category.
-This measure helps assess the spread of prices around the mean and provides insight into the degree of dispersion in price values among the observed jeans.
-
 \newpage
@@
 The linear regression seeked to determine the optimal parameters $\beta_0$ and $\beta_1$ that minimize the discrepancies between predicted and observed prices across varying pocket areas in the dataset.
-Through this minimization process, the model constructs a line that most accurately represents the association between pocket area and price.
+The model constructs a line that most accurately represents the association between pocket area and price.
 Consequently, we can predict price values based on known pocket area measurements.
@@
 Additionally, linear regression lines were overlaid for each gender group to observe potential differences in the relationship between pocket area and price (see @fig-price_per_pocket_gender).
-
-This visualization facilitated the comparison of how pocket area related to price for men's and women's jeans separately.
-By including separate regression lines for each gender, we could assess the direction and strength of the relationship between these variables within each group.
-The use of different colors for men and women aided in distinguishing between the two groups, enabling easy interpretation of the plot.
 
@@
 
-In summary, the results suggest that pocket area is not a significant predictor of price for either men's or women's jeans in the dataset analyzed.
+The results suggest that pocket area is not a significant predictor of price for either men's or women's jeans in the dataset analyzed.
 Other factors not considered in this analysis are likely to have a greater influence on the pricing of jeans for both genders.
-\newpage
+
+Furthermore, to quantify the central tendency of prices, the average price for both men's and women's jeans was calculated.
+Using the `mean()` function, it was determined that the average price for men's jeans was $81.184, while for women's jeans, it was $80.316.
+These average values offer insight into the typical price range within each gender category.
+
+In addition to the average price, the standard deviation of priceswas calculated using the `sd()` function.
+The standard deviation measures the degree of dispersion or variability in prices within each gender category.
+For women's jeans, the standard deviation of price was found to be $48.79, indicating a considerable variability in prices.
+Similarly, for men's jeans, the standard deviation was $40.49, reflecting variability within this gender category as well.
 
@@
 
-## First discussion point
+## Price Disparity in Clothing
+The pink tax refers to the phenomenon where products marketed towards girls and women are priced higher than similar products targeted towards boys and men.It represents a type of pricing gender discrimination, leading to women being charged more for items like clothing, toys, and personal care products in comparison to men (@mydoh).
 
-as mentioned before
+An example direclty applicable to clothes where the "Levi's 501 jeans for women [that] are on average 46% more expensive than the men's version" (@forbes).
+The same pair of jeans for women are priced at $98, while the men's 501 original fit jeans are $89.50 (@blackcurve).
 
-## Second discussion point
-## Third discussion point
-https://www.mydoh.ca/learn/blog/lifestyle/what-is-the-pink-tax-a-guide-for-teens/
+However, when considering the specific aspect of pocket size in jeans, the analysis reveals an interesting but inconclusive finding.
+While there appears to be a small negative association between pocket area and price for women's jeans, indicating that larger pocket sizes may be associated with slightly lower prices, this relationship is statistically insignificant.
+The analysis also demonstrates that pocket area explains only a small proportion of the variance in price for women's jeans, suggesting that other factors likely play a more significant role in determining pricing.
+
+Therefore, while pricing disparities according to gender remain a relevant financial phenomenon, the specific relationship between pocket size and price in women's jeans remains weak and inconclusive, which underscores the complexity of pricing dynamics in the fashion industry.
+
+Moreover, while the average price for women's jeans ($80.316) is slightly lower than that for men's jeans ($81.184), this finding may seem contradictory to the general notion of the pink tax, which suggests that women are typically charged more for comparable products.
+However, when considering the standard deviations calculated for both men's and women's jeans, variability in prices within each gender category becomes evident.
+The considerable standard deviation for women's jeans ($48.79) implies a wide range of prices, aligning with the idea of pricing gender discrimination and the existence of the pink tax.
+Yet, the standard deviation for men's jeans ($40.49) also indicates variability, suggesting that pricing disparities may not be exclusive to women's products.
 

### 2024-04-24 paper/paper.qmd
final paper

@@
 ---
-title: "Jean Pockets and Gender"
-subtitle: "subtitle"
+title: "Exploring Pocket Size and Jean Prices for Men and Women"
+subtitle: "An Analysis of the 2018 *Women´s Pockets are Inferior* Data"
 author: Hari Lee Robledo
